Actuator line modeling of vertical-axis turbines

### 2016-05-12 paper.tex
Slightly tweak wording for DS model speculation

Figure~\ref{fig:RM2-ALM-perf-curves} shows the performance curves computed for
the RM2 by the ALM, and those from the tow tank
experiments~\cite{Bachant2016-RM2-paper}. As with the high solidity RVAT, $C_P$
is overpredicted at high $\lambda$. However, $\lambda_0$, the tip speed ratio of
peak power coefficient, is also shifted to the right. This is indicative of
inaccurate dynamic stall modeling, which could possibly be attributed to one of
the models' tuning constants, e.g., the time constant for the lagged angle of
attack. Limited ad hoc testing revealed that $C_P$ at $\lambda_0$ was more
accurately predicted with a lagged angle of attack time constant roughly double
the default value. This could be investigated further by looking at the phase
of, e.g., maximum $C_P$ peaks compared to the experimental values (or possibly
those from blade-resolved CFD), but for the present study only mean values were
considered.

>>>>

Figure~\ref{fig:RM2-ALM-perf-curves} shows the performance curves computed for
the RM2 by the ALM, and those from the tow tank
experiments~\cite{Bachant2016-RM2-paper}. As with the high solidity RVAT, $C_P$
is overpredicted at high $\lambda$. However, $\lambda_0$, the tip speed ratio of
peak power coefficient, is also shifted to the right. This is indicative of
inaccurate dynamic stall modeling, which could possibly be attributed to one of
the models' tuning constants, e.g., the time constant for the lagged angle of
attack. Limited ad hoc testing revealed that the mean $C_P$ at $\lambda_0$ more
closely matched experimental measurements with $T_\alpha$ roughly double the
default value given in~\cite{Sheng2008}. This could be investigated further by
looking at the phase of, e.g., maximum $C_P$ peaks compared to the experimental
values (or possibly those from blade-resolved CFD), but for the present study
only mean values were considered.
